---
title: "ESM 204 - Assignment 2"
author: "Kirsten White, Van Gonzales, Max Settineri"
date: "April 24, 2022"
output: 
  html_document: 
    highlight: espresso
    theme: flatly
    toc: yes
---

```{r setup, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(janitor)
library(equatiomatic)
```


```{r}
# Read in the data
water_data <- read_csv(here("Water_Districts.csv")) %>%
  clean_names

# Re-organize the data
mc_data <- pivot_longer(data = water_data, 
                        cols = mc_kern:mc_ventura, 
                        names_to = "district", 
                        values_to = "mc") 

```

# Part 1

### Plotting Marginal Cost Curves by Irrigation District 

The dataset contains estimates of the marginal cost of reducing water usage in each of the four irrigation districts (Kern, Mojave, Antelope, and Ventura) at different levels of reduction (in Acre Feet).

For each irrigation district, plot the marginal abatement cost data (from the data provided) and estimate a linear regression model with zero intercept. These estimated linear regressions will be your estimates of the marginal abatement cost curve (one for each irrigation district), which you will use for the remainder of this analysis.

```{r, include = FALSE}
# Plot the data for each irrigation district

# All together
ggplot(data = mc_data, aes(x = reduction, y = mc))+
  geom_jitter(size = 0.5, aes(color = district))+
  theme_grey()+ 
  geom_smooth(method = "lm", aes(color = district))+
  labs(x = "Quantity of Water (Acre Feet, AF)", 
       y = "Price of Reduction ($/AF)", 
       title = "Marginal Cost Curves")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```


```{r}
# Linear models for each district with the y-intercept as zero

lm_kern <- lm(mc_kern ~ 0 + reduction, data = water_data)
lm_mojave <- lm(mc_mojave ~ 0 + reduction, data = water_data)
lm_antelope <- lm(mc_antelope ~ 0 + reduction, data = water_data)
lm_ventura <- lm(mc_ventura ~ 0 + reduction, data = water_data)

# Find slopes for each district

slope_kern <- lm_kern$coefficient[1]
slope_mojave <- lm_mojave$coefficient[1]
slope_antelope <- lm_antelope$coefficient[1]
slope_ventura <- lm_ventura$coefficient[1]

# Save the MC curve line equations for each district  
mc_kern <- function(x){lm_kern$coef*x}
mc_mojave <- function(x){lm_mojave$coef*x}
mc_antelope <- function(x){lm_antelope$coef*x}
mc_ventura <- function(x){lm_ventura$coef*x}

# Plot the MC curves

ggplot() +
  stat_function(aes(color = "Kern"), fun = mc_kern, size = 1) +
  stat_function(aes(color = "Mojave"), fun = mc_mojave, size = 1) +
  stat_function(aes(color = "Antelope"), fun = mc_antelope, size = 1) +
  stat_function(aes(color = "Ventura"), fun = mc_ventura, size = 1) +
  scale_x_continuous(name="Quantity of Water (Acre feet, AF)", limits=c(0,245),expand = c(0, 0)) +
  scale_y_continuous(name="Price of Reduction ($/AF)", limits=c(0,629),expand = c(0, 0)) +
  theme_classic() +
  labs(title = "Marginal Cost Curves by District")+
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
  
```


# Part 2

### Plotting Water Demand Curves by Irrigation District 

Using your estimated marginal abatement cost curves, derive each district’s demand curve for water. In other words, how much would each district be willing to pay for the right to use the first AF of water, second AF, etc.? Plot each district’s demand curve on a single graph.
Which sector is willing to pay the most for the first AF of water?

```{r}
# Derive District's Demand Curves for Water

# Abatement = Eo - E

# Eo provided as the baseline usage for each district

kern_baseline <- 150
mojave_baseline <- 140
antelope_baseline <- 220
ventura_baseline <- 245

# Derive each demand curve by substituting it on the previous marginal cost curves

# If Abatement = Eo - E; 

kern_mb <- function(x){343.5 - 2.29*x}
mojave_mb <- function(x){532.0 - 3.8*x}
antelope_mb <- function(x){629.2 - 2.86*x}
ventura_mb <- function(x){436.1 - 1.78*x}


# Plot Demand Curves

ggplot(data.frame(x = c(0, 250)), aes(x = x)) + 
  stat_function(aes(color = "Kern"), fun = kern_mb, size = 1) +
  stat_function(aes(color = "Mojave"), fun = mojave_mb, size = 1) +
  stat_function(aes(color = "Antelope"), fun = antelope_mb, size = 1)+
  stat_function(aes(color = "Ventura"), fun = ventura_mb, size = 1)+
  theme_minimal() +
  ylim(0, 750) +
  labs(x = "Quantity of Water, (Acre Feet, AF)", y = "Price of Reduction ($/AF)",
       title = "Demand Curves by District") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```

Based off of the graph above, Antelope is willing to pay the most for the first unit of abatement. 

# Part 3 

### Evaluating Policy Considerations

Three different policies for reducing water use among these irrigation districts will be analyzed. 

In total, these irrigation districts will need to reduce water consumption from the current 755 AF down to 500 AF. For each intervention listed below, perform the following calculations: 
(1) calculate the stringency of the policy (defined below for each intervention) required to achieve the 500 AF target, 
(2) calculate the total cost of meeting the target using that approach, 
(3) calculate the cost to each district, and 
(4) calculate the tax revenue generated.

### **Policy A - Cap Without Trade** 

Reduce each district’s water use by the same fraction (e.g., 1/3 of current baseline use), so the 500 AF target is met. Trade is not allowed. Stringency is defined as the magnitude of the fraction.


```{r}
# Stringency is the fraction by which each district has to reduce its water usage (the amount each district has to reduce will total to 500 AF)
a_stringency <- (255/755)

# Amount each district needs to abate to reach goal 
kern_use_reduction <- (a_stringency * kern_baseline)
# kern has to reduce 50.7

mojave_use_reduction  <- (a_stringency * mojave_baseline)
# mojave has to reduce 47.9

antelope_use_reduction  <- (a_stringency * antelope_baseline)
# antelope has to reduce 74.3

ventura_use_reduction  <- (a_stringency * ventura_baseline)
# ventura has to reduce 82.7

# Now we can find the new abatement values by subtracting each districts baseline water use from the amount they need to reduce by 

kern_abatement_cap <- kern_baseline - kern_use_reduction
# kern needs to abate 50.7 units from baseline 150 = 99.3
mojave_abatement_cap <- mojave_baseline - mojave_use_reduction
# mojave needs to abate 47.32 units from baseline 140 = 92.7
antelope_abatement_cap <- antelope_baseline - antelope_use_reduction
# antelope needs to abate 74.36 units from baseline 220 = 145.6
ventura_abatement_cap <- ventura_baseline - ventura_use_reduction
# ventura needs to abate 82.81 units from baseline 245 = 162.3 

# With the new quantity of water each district is allowed to use, we can find the price at this new abatement level 

# Then, to find the total cost to each district, we can plug in the reduction (new abatement quantity) into each district's cost curve (equation of the MC curve) and find the area under the line (area of a triangle)

kern_price_abatement <- (343.5-2.29*(kern_abatement_cap))
kern_cost_abatement <- (0.5 * kern_use_reduction * kern_price_abatement)
# y (P* ) = 343.5 - 2.29 (99.3) =  115.20; 
# therefore the total cost to abate is the area under the curve = (1/2 * 50.7 * 115.20) = $2,938.83
# kern total cost = $2,938.83

mojave_price_abatement <- (532.0 - 3.8*(mojave_abatement_cap))
mojave_cost_abatement <- (0.5 * mojave_use_reduction * mojave_price_abatement)
# y (P* ) = 532.0 - 3.8* (92.68) = 179.82, 
# mojave total cost = (0.5 * 179.82*47.32) = $4,248.11

antelope_price_abatement <- (629.2 - 2.86*(antelope_abatement_cap))
antelope_cost_abatement <- (0.5 * antelope_use_reduction * antelope_price_abatement)
#y (P* ) = 629.2 - 2.86* (145.64) = 212.70; 
# antelope total cost = (0.5 * 212.70 * 74.26) = $7,895.29

ventura_price_abatement <- (436.1 - 1.78*(ventura_abatement_cap))
ventura_cost_abatement <- (0.5 * ventura_use_reduction * ventura_price_abatement)
# y (P* ) = 436.1 - 1.78* (162.192) = 147, P 
# ventura total cost = (0.5 * 147 * 82.82) = $6,094.09

total_cost_abate <- kern_cost_abatement + mojave_cost_abatement + antelope_cost_abatement + ventura_cost_abatement
# the total cost of abatement for all the districts under this policy is $21,176.32
```
(1) Each district has to reduce `r round(a_stringency, 3)*100`% from their starting baseline to reach the abatement target of 500 AF.  

  - Kern reduces `r round(kern_use_reduction, 2)` units from `r kern_baseline` AF down to `r round(kern_abatement_cap, 2)` AF at a price of `r round(kern_price_abatement, 2)` $/AF. 
  - Mojave reduces `r round(mojave_use_reduction, 2)` units from `r mojave_baseline` AF down to `r round(mojave_abatement_cap, 2)`AFat a price of `r round(mojave_price_abatement, 2)` $/AF.
  - Antelope reduces `r round(antelope_use_reduction, 2)` units from `r antelope_baseline` AF down to `r round(antelope_abatement_cap, 2)` AF at a price of `r round(antelope_price_abatement, 2)` $/AF.
  - Ventura reduces `r round(ventura_use_reduction, 2)` units from `r ventura_baseline` AF down to `r round(ventura_abatement_cap, 2)` AF at a price of `r round(ventura_price_abatement, 2)` $/AF.
  

(2) The overall total cost is: 
  - $`r round(total_cost_abate, 2)`

(3) The total cost to each district under this cap with no trade policy is: 

  - Kern: $`r round(kern_cost_abatement, 0)`

  - Mojave: $`r round(mojave_cost_abatement, 0)`

  - Antelope: $`r round(antelope_cost_abatement, 0)`

  - Ventura: $`r round(ventura_cost_abatement, 0)`
  

(4) No tax revenue is generated with the Cap without Trade policy


    

### **Policy B - Tax on Water Usage**

A single tax is implemented on all water use in each of the four districts, such that water use is reduced to the 500 AF target. Stringency is defined as the magnitude of the tax.

To evaluate the tax needed to achieve a use target of 500 AF, we must compute the aggregate marginal cost curve and calculate the correspondent $/AF for that reduction (255 AF).

```{r}
# step 1: Find the MC Aggregate demand by adding up the inverse slopes of each district's marginal cost curve

mc_aggregate_slope <- (1/slope_kern + 1/slope_mojave + 1/slope_antelope + 1/slope_ventura)
# MC Aggregate = 1.61Q

# step 2: find the tax at the target abatement level of 255

tax_target <- 255/mc_aggregate_slope
# tax is $158.07

# step 3: find the amount of water usage each district needs to reduce by at this tax level (by plugging in the tax and solving for the new abatement quantity) 

kern_abatement_tax <- tax_target/slope_kern
# kern needs to abate 69.13 units
mojave_abatement_tax <- tax_target/slope_mojave
# mojave needs to abate 41.55 units
antelope_abatement_tax <- tax_target/slope_antelope
# antelope needs to abate 55.31 units
ventura_abatement_tax <- tax_target/slope_ventura
# ventura needs to abate 88.99 units

# step 4: find the total cost to each district (using new abatement level and tax)

kern_cost_tax <- (0.5 * tax_target * kern_abatement_tax)
# it will cost kern 5463.93 
mojave_cost_tax <- (0.5 * tax_target * mojave_abatement_tax)
# it will cost mojave 3284.04
antelope_cost_tax <- (0.5 * tax_target * antelope_abatement_tax)
# it will cost antelope 4371.64
ventura_cost_tax <- (0.5 * tax_target * ventura_abatement_tax)
# it will cost ventura 7033.93

# step 5: sum each district cost to find the total cost 
total_cost_tax <- (kern_cost_tax + mojave_cost_tax + antelope_cost_tax + ventura_cost_tax)

# step 6: find total tax revenue generated
# should be ~79k
# calculate the amount each district is still using by the tax level (baseline - reduction)*tax)

kern_tax_revenue <- ((kern_baseline-kern_abatement_tax)*tax_target)
# kern tax revenue: 12782.18
mojave_tax_revenue <- ((mojave_baseline-mojave_abatement_tax)*tax_target)
# mojave tax revenue: 15561.29
antelope_tax_revenue <- ((antelope_baseline-antelope_abatement_tax)*tax_target)
# antelope tax revenue: 26031.44
ventura_tax_revenue <- ((ventura_baseline-ventura_abatement_tax)*tax_target)
ventura_tax_revenue
# ventura tax revenue: 24658.53

total_tax_revenue <- (kern_tax_revenue + mojave_tax_revenue +antelope_tax_revenue + ventura_tax_revenue)
# total tax revenue: 79033.44

```
(1) The stringency under this policy is a tax of $`r round(tax_target, 2)`

(2) The overall total cost of this tax policy is: 
    - $`r round(total_cost_tax, 4)`

(3) The total cost to each district under this tax policy is: 

  - Kern: $`r round(kern_cost_tax, 0)`

  - Mojave: $`r round(mojave_cost_tax, 0)`

  - Antelope: $`r round(antelope_cost_tax, 0)`

  - Ventura: $`r round(ventura_cost_tax, 0)`

  
(4) Total tax revenue generated is: 
  - $`r round(total_tax_revenue)`


### **Policy C - Cap and Trade**
Cap water use as in part (a), but after those caps are set, allow trade across districts. How much water is used by each district after trade? Stringency is the same as in part (a).

Under this policy, the overall stringency will be the same as Policy A - 33.8%. Districts will trade water usage rights until there marginal costs of abatement are equal. There will be no tax revenue generated. Di

The equimarginal principle tells us that units will be bought and sold at the same tax rate as calculated in Policy B ($158.07). Therefore, the total cost of meeting the 500 AF abatement target using a Cap and Trade policy will be the same as the cost under the Tax policy,  $21,1763.16.  

To calculate the cost per district, we must first determine water usage under cap and trade for each district for both pre, and post trade. Pre trade water usage levels are equal to those calculated in part A under the cap and no trade policy. Post trade water usage levels are equal to those calculated in part B under taxation. Districts 
- **Kern:** Pre trade = `r round(kern_use_reduction, 2)`; Post trade = `r round(kern_abatement_tax, 2)`
- **Mojave:** Pre trade = `r round(mojave_use_reduction, 2)`; Post trade = `r round(mojave_abatement_tax, 2)`
- **Antelope:** Pre trade = `r round(antelope_use_reduction, 2)`; Post trade = `r round(antelope_abatement_tax, 2)`
- **Ventura:** Pre trade = `r round(ventura_use_reduction, 2)`; Post trade = `r round(ventura_abatement_tax, 2)`

**Cost per district**
- **Kern:** Initial cost of abatement = $`r round(kern_cost_tax, 2)`. Kern's difference in pre and post trade water use is `r (round(kern_use_reduction, 2) - round(kern_abatement_tax, 2))`. Kern sells this differential to other districts for the price of 18.47*158.07 = 2,919.44. Therefore, Kern's total cost is \$`r round(kern_cost_tax, 2) - 2919.44`
- **Mojave:** Initial cost of abatement = $`r round(mojave_cost_tax, 2)`. Mojave's difference in pre and post trade water use is `r (round(mojave_use_reduction, 2) - round(mojave_abatement_tax, 2))`. Mojave buys this differential from other districts for the price of 5.73*158.07 = 905.74. Therefore, Mojaves's total cost is \$`r round(mojave_cost_tax, 2) + 905.74`
- **Antelope:** Initial cost of abatement = $`r round(antelope_cost_tax, 2)`. Antelope's difference in pre and post trade water use is `r (round(antelope_use_reduction, 2) - round(antelope_abatement_tax, 2))`. Antelope buys this differential from other districts for the price of 18.99*158.07 = 3,001.75. Therefore, Antelope's total cost is \$`r round(antelope_cost_tax, 2) + 3001.75`
- **Ventura:** Initial cost of abatement = $`r round(venture_cost_tax, 2)`. Ventura's difference in pre and post trade water use is `r (round(ventura_use_reduction, 2) - round(ventura_abatement_tax, 2))`. Ventura sells this differential to other districts for the price of 6.25*158.07 = 987.94. Therefore, Ventura's total cost is \$`r round(ventura_cost_tax, 2) - 987.94`

# Part 4

A severe drought hits California, and it is necessary to reduce water use from 500 AF down to 300 AF. Your job is to estimate the cost of the drought (i.e., the cost of reducing water use from 500 AF to 300 AF) to each irrigation district under each policy. Considering the entire jump from status quo (755 AF) to the drought (300 AF), which policy is preferred by each irrigation district? How does your answer depend on how rights are allocated to each district (in policies (a) and (c))? 

### **Policy A - Cap Without Trade** 

```{r}
# Stringency is the fraction by which each district has to reduce its water usage (the amount each district has to reduce will total to 300 AF)
four_stringency <- (200/500)

# Amount each district needs to abate to reach goal 
kern_300_use_reduction <- (four_stringency * kern_abatement_cap)
# kern has to reduce 39.74

mojave_300_use_reduction  <- (four_stringency * mojave_abatement_cap)
# mojave has to reduce 37.09

antelope_300_use_reduction  <- (four_stringency * antelope_abatement_cap)
# antelope has to reduce 58.28

ventura_300_use_reduction  <- (four_stringency * ventura_abatement_cap)
# ventura has to reduce 64.90

# Now we can find the new abatement values by subtracting each districts baseline water use from the amount they need to reduce by 

kern_300_abatement_cap <- kern_abatement_cap - kern_300_use_reduction
# kern needs to abate 39.74 units from baseline 99.3 = 59.60
mojave_300_abatement_cap <- mojave_abatement_cap - mojave_300_use_reduction
# mojave needs to abate 37.09 units from baseline 92.7 = 55.63
antelope_300_abatement_cap <- antelope_abatement_cap - antelope_300_use_reduction
# antelope needs to abate 58.28 units from baseline 145.60 = 87.42
ventura_300_abatement_cap <- ventura_abatement_cap - ventura_300_use_reduction
# ventura needs to abate 64.90 units from baseline 162.3 = 97.35

# With the new quantity of water each district is allowed to use, we can find the price at this new abatement level 

# Then, to find the total cost to each district, we can plug in the reduction (new abatement quantity) into each district's cost curve (equation of the MC curve) and find the area under the line (area of a triangle)

kern_300_price_abatement <- (343.5-2.29*(kern_300_abatement_cap))
kern_300_cost_abatement <- (0.5 * kern_300_use_reduction * kern_300_price_abatement)
# y (P* ) = 343.5 - 2.29 (59.60) =  207.01; 
# therefore the total cost to abate is the area under the curve = (1/2 * 39.74 * 207.01) = $4,112.78
# kern total cost = $4,112.78

mojave_300_price_abatement <- (532.0 - 3.8*(mojave_300_abatement_cap))
mojave_300_cost_abatement <- (0.5 * mojave_300_use_reduction * mojave_300_price_abatement)
# y (P* ) = 532.0 - 3.8* (55.63) = 320.61, 
# mojave total cost = (0.5 * 320.61*37.09) = $5,945.07

antelope_300_price_abatement <- (629.2 - 2.86*(antelope_300_abatement_cap))
antelope_300_cost_abatement <- (0.5 * antelope_300_use_reduction * antelope_300_price_abatement)
#y (P* ) = 629.2 - 2.86* (87.42) = 379.19; 
# antelope total cost = (0.5 * 379.19 * 58.28) = $11,049.15

ventura_300_price_abatement <- (436.1 - 1.78*(ventura_300_abatement_cap))
ventura_300_cost_abatement <- (0.5 * ventura_300_use_reduction * ventura_300_price_abatement)
# y (P* ) = 436.1 - 1.78* (97.35) = 262.82
# ventura total cost = (0.5 * 262.82 * 97.35) = $8,528.44

total_300_cost_abate <- kern_300_cost_abatement + mojave_300_cost_abatement + antelope_300_cost_abatement + ventura_300_cost_abatement
# the total cost of abatement for all the districts under this policy is $29,635.44
```

(1) Each district has to reduce `r round(four_stringency, 3)*100`% from their starting baseline to reach the abatement target of 300 AF.  

  - Kern reduces `r round(kern_300_use_reduction, 2)` units from `r round(kern_abatement_cap, 2)` AF down to `r round(kern_300_abatement_cap, 2)` AF at a price of `r round(kern_300_price_abatement, 2)` $/AF. 
  - Mojave reduces `r round(mojave_300_use_reduction, 2)` units from `r round(mojave_abatement_cap, 2)` AF down to `r round(mojave_300_abatement_cap, 2)`AF at a price of `r round(mojave_300_price_abatement, 2)` $/AF.
  - Antelope reduces `r round(antelope_300_use_reduction, 2)` units from `r round(antelope_abatement_cap, 2)` AF down to `r round(antelope_300_abatement_cap, 2)` AF at a price of `r round(antelope_300_price_abatement, 2)` $/AF.
  - Ventura reduces `r round(ventura_300_use_reduction, 2)` units from `r round(ventura_abatement_cap, 2)` AF down to `r round(ventura_300_abatement_cap, 2)` AF at a price of `r round(ventura_300_price_abatement, 2)` $/AF.
  

(2) The overall total cost is: 
  - $`r round(total_300_cost_abate,2)`

(3) The total cost to each district under this cap with no trade policy is: 

  - Kern: $`r round(kern_300_cost_abatement, 0)`

  - Mojave: $`r round(mojave_300_cost_abatement, 0)`

  - Antelope: $`r round(antelope_300_cost_abatement, 0)`

  - Ventura: $`r round(ventura_300_cost_abatement, 0)`
  
### **Policy B - Tax on Water Usage**

```{r}
# step 1: use the aggregate slope calculated in part 3 to find the tax target at 300 AF of water usage

tax_target_300 <- 455/mc_aggregate_slope
# tax is $282.04

# step 2: find the amount of water usage each district needs to reduce by at this tax level (by plugging in the tax and solving for the new abatement quantity) 

kern_300_abatement_tax <- tax_target_300/slope_kern
# kern needs to abate 123.36 units
mojave_300_abatement_tax <- tax_target_300/slope_mojave
# mojave needs to abate 74.14 units
antelope_300_abatement_tax <- tax_target_300/slope_antelope
# antelope needs to abate 98.70 units
ventura_300_abatement_tax <- tax_target_300/slope_ventura
# ventura needs to abate 158.80 units

# step 3: find the total cost to each district of abating from 755 to 300 AF

kern_cost_tax_300 <- (0.5 * tax_target_300 * kern_300_abatement_tax)
# it will cost kern 17395.91 
mojave_cost_tax_300 <- (0.5 * tax_target_300 * mojave_300_abatement_tax)
# it will cost mojave 10455.63
antelope_cost_tax_300 <- (0.5 * tax_target_300 * antelope_300_abatement_tax)
# it will cost antelope 13918.31
ventura_cost_tax_300 <- (0.5 * tax_target_300 * ventura_300_abatement_tax)
# it will cost ventura 22394.46

# step 4: since the question asks for the cost of abatement from 500 to 300, we then subtract the total cost to each district found in question 3b from the total costs found above.

kern_cost_tax_500_300 <- (kern_cost_tax_300 - kern_cost_tax)
# it will cost kern 11931.98 
mojave_cost_tax_500_300 <- (mojave_cost_tax_300 - mojave_cost_tax)
# it will cost mojave 7171.596
antelope_cost_tax_500_300 <- (antelope_cost_tax_300 - antelope_cost_tax)
# it will cost antelope 9546.68
ventura_cost_tax_500_300 <- (ventura_cost_tax_300 - ventura_cost_tax)
# it will cost ventura 15360.53

# step 5: sum each district cost to find the total cost 
total_cost_tax_300 <- (kern_cost_tax_500_300 + mojave_cost_tax_500_300 + antelope_cost_tax_500_300 + ventura_cost_tax_500_300)

```

The overall total cost of this tax policy is: 
    - $`r round(total_cost_tax_300, 4)`

The total cost to each district under this tax policy is: 

  - Kern: $`r round(kern_cost_tax_500_300, 0)`

  - Mojave: $`r round(mojave_cost_tax_500_300, 0)`

  - Antelope: $`r round(antelope_cost_tax_500_300, 0)`

  - Ventura: $`r round(ventura_cost_tax_500_300, 0)`

### **Policy C - Cap and Trade**

The equimarginal principle tells us that units will be bought and sold at the same tax rate as calculated in Policy B ($282.04). Therefore, the total cost of meeting the 300 AF abatement target using a Cap and Trade policy will be the same as the cost under the Tax policy,  $44,010.78. 



### Which Policy is Preferred?
**Table 1**

```{r}
District  = c("Kern", "Mojave", "Antelope", "Ventura")
Cap_No_Trade = c("7,052", "10,193", "18,944", "14,622")
Tax = c("17,396", "10,456", "13,919", "22,395")
Cap_and_Trade = c("-", "-", "-", "-")

df <- data.frame(District, Cap_No_Trade, Tax, Cap_and_Trade)

df
                  
```

Part 3 calculates the cost of abatement of reducing total water usage from 755 to 500 AF for each district. Part 4 calculates the cost of abatement of reducing total water usage from 500 to 300 AF for each district. Table 1  displays the total costs of abatement from 755 to 300 AF for each district by policy. As displayed, for all districts except Antelope, the "Cap No Trade" policy will be the least costly. However, Antelope will prefer the tax. 
